Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-06-01 Robustness-Methods-and-Results.Rmd
mlcor tbl lab fix

vars_full <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  "Outgroup Interaction" = "OutgroupInteraction",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

@@

vars_out <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  "Practical Need" = "practical_need_dum",
  "Psychological Need" = "psychological_need_dum",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

s1_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 1, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s2_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 2, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s3_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(study == 3, OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
all_MlCor_out <- 
  MlCorMat(
    data = dt_goal_directedness %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  )

>>>>

vars_full <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  #"Outgroup Interaction" = "OutgroupInteraction",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

@@

vars_out <- c(
  "Core Need" = "CoreNeed",
  "Competence" = "Competence",
  "Autonomy" = "Autonomy",
  "Relatednesss" = "Relatednesss",
  # "Practical Need" = "practical_need_dum",
  # "Psychological Need" = "psychological_need_dum",
  "Accidental" = "InteractionAccidental",
  "Quality" = "Quality",
  "Attitudes NL" = "Attitude"
)

s1_MlCor_out <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 1, OutgroupInteractionLab == "Yes", PID != 21), # PP 21 has inflated zero for Accidental
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s2_MlCor_out <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
s3_MlCor_out <- 
  MlCorMat(
    data = dt_exp_all %>% filter(study == 3, OutgroupInteractionLab == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  ) 
all_MlCor_out <- 
  MlCorMat(
    data = dt_exp_all %>% filter(OutgroupInteractionLab == "Yes"),
    id = "PID",
    selection = as.character(vars_out),
    labels = names(vars_out)
  )
